A Streaming Algorithm for 2-Center with Outliers in High Dimensions

### 2015-04-28 paper.tex
Minor update

\title{A Streaming Algorithm for 2-Center with Outliers in High Dimensions}
%\title{Computing 2-Center with Outliers on High-Dimensional Data Streams}
\author{Behnam~Hatami\thanks{Department of Computer Engineering, 
	Sharif University of Technology.
	{\tt hatami@ce.sharif.edu}}
	\and 
	Hamid~Zarrabi-Zadeh\thanks{Department of Computer Engineering, 
	Sharif University of Technology.
	{\tt zarrabi@sharif.edu}}
}

@@

If $|B_2| \geq \dz$, then $c_p$ is the centerpoint of the first $\dz$ points currently in $B_2$. in this case, we add all of $B_2$ points to $B_1$. Due to variant (b), $r \leq \delta/2 < \delta^*/2$. So By Lemma \ref{obs:center-point} then $$ By Lemma \ref{lem:} By contradiction assume that $B_2 \cap B_2^* \neq \emptyset$. If $c_p \in B_2^*$, then by variant (b), $B(c_p, \frac{2 \len{c_1 c_p}}{\alpha}) \subset B(c_2, r)$
}
\item [(d)] {
	\begin{enumerate}
		\item [1.]{
		Due to  Observation \ref{obs:c+4}, if $c_1 \in B_1^*$ and $c_p \in B_2^*$ then $1 \leq \frac{\len{c_1 c_p}}{\delta^*} \leq \frac{\len{c_1 c_p}}{\alpha r^*}$ and as a result $2r^* \leq \frac{2 \len{c_1c_p}}{\alpha}$.

@@

\begin{lemma}
\label{lem:}
	After termination of \Cref{alg:case-1}, 
	if $|B_2| \ge \dz$ and $\cp \not\in B_2^*$,
	then $B_2 \cap B_2^* = \emptyset$.
\end{lemma}

\begin{proof}
	TBA.
\end{proof}

>>>>

\title{A Streaming Algorithm for 2-Center with Outliers in High Dimensions}
%\title{Computing 2-Center with Outliers on High-Dimensional Data Streams}
\author{Behnam~Hatami\thanks{Department of Computer Engineering, 
	Sharif University of Technology.
	{\tt bhatami@ce.sharif.edu}}
	\and 
	Hamid~Zarrabi-Zadeh\thanks{Department of Computer Engineering, 
	Sharif University of Technology.
	{\tt zarrabi@sharif.edu}}
}

@@

If $|B_2| \geq \dz$, then $c_p$ is the centerpoint of the first $\dz$ points currently in $B_2$. in this case, we add all of $B_2$ points to $B_1$. Due to variant (b), $r \leq \delta/2 < \delta^*/2$. So By Lemma \ref{obs:center-point} then $c_p \in B_1^*$ or $c_p \in B_2^*$. By cantradiction assume that $c_p \in B_2^*$.
}
\item [(d)] {
	\begin{enumerate}
		\item [1.]{
		Due to  Observation \ref{obs:c+4}, if $c_1 \in B_1^*$ and $c_p \in B_2^*$ then $1 \leq \frac{\len{c_1 c_p}}{\delta^*} \leq \frac{\len{c_1 c_p}}{\alpha r^*}$ and as a result $2r^* \leq \frac{2 \len{c_1c_p}}{\alpha}$.

@@

% \begin{lemma}
% \label{lem:}
%	After termination of \Cref{alg:case-1}, 
%	if $|B_2| \ge \dz$ and $\cp \not\in B_2^*$,
%	then $B_2 \cap B_2^* = \emptyset$.
%\end{lemma}

%\begin{proof}
%	TBA.
%\end{proof}
